Final Fantasy-\/style Role-\/\+Playing Game about the non-\/heroic non-\/player characters inhabiting the world in a traditional example of such a game. Multiplatform via Simple Directmedia Layer (S\+D\+L2) C++ Library. Also uses Boost.

Requires the following libraries\+: S\+D\+L2 (\href{https://www.libsdl.org/download-2.0.php}{\tt https\+://www.\+libsdl.\+org/download-\/2.\+0.\+php}) S\+D\+L2\+\_\+\+Image (\href{https://www.libsdl.org/projects/SDL_image/}{\tt https\+://www.\+libsdl.\+org/projects/\+S\+D\+L\+\_\+image/}) S\+D\+L2\+\_\+ttf (\href{https://www.libsdl.org/projects/SDL_ttf/}{\tt https\+://www.\+libsdl.\+org/projects/\+S\+D\+L\+\_\+ttf/}) Boost (\href{http://sourceforge.net/projects/boost/files/latest/download?source=files}{\tt http\+://sourceforge.\+net/projects/boost/files/latest/download?source=files})

Code by Samuel Weber (sbweber). npc-\/game.\+rar contains a playable, self-\/contained, current Windows release build of the game.

Default Controls\+: Arrow keys\+: Move around the map. z\+: Interact with things on the map. esc\+: Go back/up a layer. Currently unused. f4\+: Quit the program from anywhere. F12\+: Go to the title screen. Click on a tile on the map to move to it. Click on a sprite to interact with it. To advance text, press any key or click anywhere in the window.

Debug Controls\+: 1\+: Load map \char`\"{}0,0.\+txt\char`\"{}. 2\+: Load map \char`\"{}0,1.\+txt\char`\"{}. 9\+: Go to the key rebind menu. f\+: Go to the test case for battles. Currently locks you into the battle state with no way out except the debug controls.

Explanation of Licenses\+: L\+I\+C\+E\+N\+SE is the (M\+IT) license for this project itself. L\+I\+C\+E\+N\+S\+E-\/\+S\+D\+L2 is the (zlib) license for the S\+D\+L2 library. L\+I\+C\+E\+N\+S\+E.\+md is the (M\+IT) license for the Find\+S\+D\+L2$\ast$.cmake files, the C\+Make\+Lists.\+txt (further modified from its original version), and some scattered code throughout the project (this project began its life by following the Twinklebear\+Dev S\+DL 2.\+0 Lessons, from here \href{https://github.com/Twinklebear/TwinklebearDev-Lessons}{\tt https\+://github.\+com/\+Twinklebear/\+Twinklebear\+Dev-\/\+Lessons}). Copyright.\+txt is the (B\+SD 3-\/clause) license for the Boost libraries. 